\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
Add download manager

>>>>

The download manager is the top-level client interface for peer-to-peer
downloads. It provides an API where the client can provide a hash, and
optionally, a fallback HTTP URL, and the download manager will asynchronously
download the content associated with the hash and call a user-provided callback
function when finished. The download manager implements reliable download,
preferring peer-to-peer over HTTP when possible.
